\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot,
    top=2 cm,
    bottom=2 cm,
    left=2 cm,
    right=2 cm,
    footskip=1.0 cm
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 0, 0}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={ Matheus Bruno de Moraes },
    pdfauthor={ Matheus Bruno de Moraes },
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[pscoord]{eso-pic}
\usepackage{calc}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}

% Ensure that generate pdf is machine readable/ATS parsable:
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage{charter}

% Some settings:
\raggedright
\AtBeginEnvironment{adjustwidth}{\partopsep0pt}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\topskip}{0pt}
\setlength{\columnsep}{0.15cm}
\pagenumbering{gobble}

\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]

\titlespacing{\section}{
    -1pt
}{
    0.3 cm
}{
    0.2 cm
}

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.10 cm,
        parsep=0.10 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=0 cm + 10pt
    ]
}{\end{itemize}}

\newenvironment{onecolentry}{
    \begin{adjustwidth}{
        0 cm + 0.00001 cm
    }{
        0 cm + 0.00001 cm
    }
}{\end{adjustwidth}}

\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\linespread{1.5}
}{\par\kern\topsep}

\begin{document}

\begin{header}
\textbf{MATHEUS BRUNO DE MORAES} \\
Support Engineer | DevOps | Technical Implementation \\
+55 (41) 9 9575-7856 | mbrunomoraes97@gmail.com | \href{https://github.com/brunomoraes97}{https://github.com/brunomoraes97} | \href{https://www.linkedin.com/in/brunomoraes97/}{https://www.linkedin.com/in/brunomoraes97/} \\
Brazilian, 28 years old
\end{header}

\section*{SUMMARY}
Experienced Support and DevOps Engineer with a proven track record in managing the entire customer lifecycle, from triage to complex resolution. Expertise in Linux systems administration, scripting (Bash, Python), Git, and CI/CD.  Proven ability to translate complex business needs into technical solutions and drive initiatives from concept to completion.  Strong collaboration skills fostering alignment across functions for optimized customer experiences.

\section*{SKILLS}
\begin{itemize}
\item Linux Systems Administration:  Proficient in Linux server administration, performance troubleshooting, diagnostic tools, and Docker.
\item DevOps and CI/CD: Expertise in implementing CI/CD pipelines (GitHub Actions), managing staging and production environments, Git, GitHub, Openshift and Kubernetes.
\item Programming Languages:  Proficient in Bash, Python, Java, C, Javascript, Ruby.
\item Automation and Scripting: Experienced in automating processes with Selenium, Playwright, Puppeteer, and API integrations.
\item Technical Support and Customer Experience:  Excellent communication skills, focused on customer resolution (API, S2S, platform) and knowledge base building.
\item Content Creation:  Proficient in creating technical documentation, tutorials, and support content.
\item Databases:  Experienced with MySQL (queries, data processing).
\item Security and Compliance:  Understanding of information security and compliance concepts (OffSec).
\item Tools:  Proficient in Git, GitHub, Postman, Zendesk, Jira, Zapier, N8N, and CRMs.
\end{itemize}

\section*{PROFESSIONAL EXPERIENCE}

\subsection*{Technical Onboarding Manager at IREV}
\textit{Limassol, Cyprus (Remote, full-time) | 2024-Current}
\begin{itemize}
\item Spearheaded client onboarding, managing technical setups, timelines, and stakeholder alignment.
\item Conducted scoping calls to assess customer infrastructure and plan accurate implementations.
\item Troubleshooted API, S2S, and platform integrations, collaborating with product and engineering teams.
\item Standardized documentation and streamlined onboarding processes, improving support content.
\end{itemize}

\subsection*{L2 Technical Support Engineer and Automation Specialist at Multilogin}
\textit{Tallinn, Estonia (Remote) | 2023-2024}
\begin{itemize}
\item Resolved complex technical issues through analytical problem-solving and automation.
\item Developed automation scripts (Selenium, Playwright, Puppeteer) to enhance customer support.
\item Processed data and performed queries in MySQL.
\item Created technical documentation and demonstration videos for user empowerment.
\end{itemize}


\subsection*{Software Engineer at SaasPro}
\textit{Curitiba, Brazil (In-person) | 2022-2023}
\begin{itemize}
\item Managed professional services outside of product scope.
\item Developed and maintained platform integrations for process optimization.
\item Implemented chatbot and AI-based solutions for customer engagement.
\item Worked with web frameworks (Flask, FastAPI, Django).
\item Provided technical guidance during sales calls and development strategy.
\end{itemize}

\subsection*{Technical Support Engineer at SaasPro}
\textit{Curitiba, Brazil (In-person) | 2019-2023}
\begin{itemize}
\item Provided technical support via email, chat, and calls, ensuring customer satisfaction.
\item Guided clients on email compliance best practices.
\item Integrated various tools via API (Python, Zapier, Make).
\item Collaborated with teams to address customer needs and feedback.
\end{itemize}


\section*{EDUCATION}
\subsection*{Bachelor’s in Information and Communication Technologies (ICT)}
\textit{Universidade Federal de Santa Catarina (UFSC), Brazil | Currently Enrolled}
\begin{itemize}
\item Teaching assistant for Algorithms and Programming (Python focus).
\item Member of the Artificial Intelligence League (LIA).
\item Focused on Object-Oriented Programming (OOP), Java, and Python.
\item Participated in the OffSec extension group, specializing in information security.
\end{itemize}

\subsection*{Bachelor’s in Psychology}
\textit{Universidade Federal do Paraná (UFPR), Brazil | Graduated in 2023}
\begin{itemize}
\item Founded and led the Neuropsychology Academic League, developing research skills.
\item Participated in cognitive rehabilitation community outreach projects.
\end{itemize}

\section*{LANGUAGES}
\begin{itemize}
\item English: Fluent
\item Portuguese: Native
\item Spanish: Intermediate
\end{itemize}

\end{document}